### 2018-10-05 paper/paper.tex
definitions mean demand deviation and average release quantity

\begin{lemma}
  The interconnection between \WIP{}-level (and also lead time for that sake), and the release
  pattern is not necessary to observe the systematic releasing misbehavior called lead time
  syndrome.
\end{lemma}

@@

% The above lemma thus specifies that for higher standard deviation in the demand higher fluctuations
% in the release pattern are sensible.
Thus, the scaled deviations in the demand specify a natural
lower-bound of release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
demand as measure for determining the time span of the release decisions and \WIP{}-levels being
considered in the analysis.
%
% Recall that the standard deviation measures the expected deviation of
% the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%
Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the \emph{time span considered} $\tsc{p}$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \tsc{p} \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate

The reduce the impact of outliers we average the actual releases over $\tsc{p}$ values.

>>>>

\begin{lemma}
  The interconnection between \WIP{}-level (and thus also the lead time for that sake), and the
  release pattern is not necessary to observe the systematic releasing misbehavior called lead time
  syndrome.
\end{lemma}

@@

% The above lemma thus specifies that for higher standard deviation in the demand higher fluctuations
% in the release pattern are sensible.
Thus, the deviations of the demand in relation to the mean specify a proportional % natural
lower-bound of release decisions to consider in the analysis of the \LTS{}.
%
Hence, we use the standard deviation $\sigma$ of the random variable $\X$ related to the mean demand
as measure for determining the time span of the release decisions and \WIP{}-levels being considered
in the analysis.
%
% Recall that the standard deviation measures the expected deviation of
% the mean in orders.
%
%
% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
% decisions from one period to the next.
%

\MS{2 definitions. 1. How many periods to average using $\sigma$. 2. How many periods to look back
  for the time: season length. }

\begin{definition}
  We define the \emph{\mddname{}} $\mdd{p}$ of period $p$ and the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \mdd{p} \defsym 1 +
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}  +
    \frac{\max \{|f(i)-f(i+1)|\ \mid \ \forall 0 \leqslant i \leqslant p \}}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}

\begin{definition}
  The \emph{\avgrqname} $\avgrq{p}$ of period $p$ is defined as
  \begin{align*}
    \avgrq{p} \defsym \frac{1}{K} \cdot \sum_{i=p-K}^{p-1}{ \ri{i}{i+1} }\tcom
  \end{align*}

  where $K=\min(p,\ceil{\mdd{p}})$.
\end{definition}

\MS{TODO: same for \WIP{}}

Intuitively the \mddname{} is a measure of variability and shift of the mean in the demand stream
with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
\mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
\textsl{\mddname{}}-average slopes over time.

% Maybe here an example?

However,

This time factor

Futhermore,... \MS[t]{seasonal stuff}
%

\begin{definition}
  We define the \emph{time span} $\ts{p}$ in period $p$ of the manufacturing system
  % with the periodised demand $\dper{\cdot}$
  under investigation as
  \begin{align*}
    \ts{p} \defsym 1 + % \ceil[\Bigg]{
    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
    % }
    +
    \MS[t]{\text{seasonal stuff}} \tcom
  \end{align*}
  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
  $3$ respectively.
  % This
  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
  % to the ceiling function
  % For asymmetric
  % probability distributions, the definition can be easily extended to integrate
\end{definition}

To reduce the impact of outliers we average the actual releases over $\ts{p}$ values.
